Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-10 Response to reviewers.tex

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#1}

\noindent \emph{There are some issues needed to be addressed further:} \\

\noindent (1) \emph{Generally speaking, predicting sales is regarded as a regression problem (numerical output) rather than classification (categorical one). Both CFS and RelieFF are originally designed for classification problem. When CFS is used for regression, please to introduce how to estimate correlations between each feature and output (total sales). Since RReliefF, as a variant of ReliefF, is special for regression, why do not the authors use RReliefF? }

\begin{verbatim}
In all our experiments we have applied  WEKA's implementation 
of the ReliefF algorithm in the regression problems. 
This version is called "Regressional ReliefF" or "RReliefF" for 
short, which was first introduced and implemented by Robnik-Sikonja 
and Kononenko (in ref. [38] for numeric targets). 
Therefore, we have clarified this point in the text to remove 
any ambiguity (see page 7, second column, and page 13 first paragraph).

For CSF, estimating the correlation between attributes is 
standard linear (Pearson's) correlation. The details have 
been added to the text to clarify this point (see page 7, 
second column, and page 13 first paragraph).
\end{verbatim}

@@

~\\
\noindent (2) \emph{In sub-section 4.2, five methods are introduced, i.e.,M5P,kNN,RF,LR and SVM. In sub-section 5.1, why is MLP (multi-layer perceptron) with one hidden layer described ?}

\begin{verbatim}
The current paper includes in sub-section 4.2 six methods: M5P, kNN, 
RF, LR, SVM, MLP, and ELM (requested by Reviewer #2). After having 
included ELM, new references have been added (the list of new 
references can be found at the end of this letter).

Moreover, as suggested by Reviewer #2 (see his/her first comment), 
the results obtained with the last two methods have been included and 
analyzed in this new version of the paper.

The ELM and MLP descriptions can be found in page 10, first paragraph.
Obtained results have been shown in Figures 2, 4, 5, 6, and in tables
in the appendix.
\end{verbatim}

@@

~\\
\noindent (2) \emph{For RF, how many trees are set? }

\begin{verbatim}
As far as the number of trees is concerned, in the experiments 
section, when describing the parameter settings, it has been 
mentioned that the best performance was obtained with a number of 
trees equal to 50 (see page 11, second paragraph of subsection 5.1).
\end{verbatim}

@@

~\\
\noindent (3) \emph{As we known, tree-based methods (e.g., M5P and RF) themselves embed feature selection procedure. That is, some features are chosen to build trees. It is not fair enough to compare five methods in Table 3. }

\begin{verbatim}
Although we agree with the reviewer's comment, and the RF and M5P 
have an embedded feature selection mechanism, we believe that it 
is unfair to compare them with the filter based feature selection 
methods we have deployed in our research. 
The aim is simply to show to the decision maker what are the possible 
results when we apply one of the off-the-shelf classifiers available 
in a common open source framework such as WEKA. 
Moreover, it is not uncommon in the literature to see such comparison 
between classifiers, as in the paper:
  M. Fernandez-Delgado, E. Cernadas, S. Barro, and D. Amorim. 2014. 
  Do we need hundreds of classifiers to solve real world 
  classification problems?. J. Mach. Learn. Res. 15, 1, pp.3133-3181
which incorporates a general comparison between all these classifiers.

This has been clarified in the text with the following sentence, at 
the end of section 5.2 (page 12, second column):

"It is important to note that both RF and M5P have an embedded feature 
selection mechanism (the variables which compose the final trees), 
however this is part of their inherent procedure. In the following 
section we will apply three filter-based feature selection techniques 
on the dataset, so all the methods will profit."
\end{verbatim}

@@

~\\
\noindent (4) \emph{It seems more reasonable to organize and write that paper according to regression viewpoint only. }

\begin{verbatim}
In agreement with reviewer’s comment, we have revised the whole paper 
remarking the regression topic present on the work. We have clarified 
in several paragraphs along the text that the problem has been 
addressed by means of regression methods (for instance, note the new 
title of Section 4.2), or we have generally referred to the term 
`regression' instead of `classification', in order to better suit 
the regression viewpoint.

@@

Moreover this suggestion have been also addressed solving the issue 
related to comment #1, where the application procedure of feature 
selection methods for regression problems has been clarified. 
\end{verbatim}

~\\
\noindent (5) \emph{It is necessary to write that paper more concisely. }

\begin{verbatim}
Following reviewer's suggestion we have reorganized some parts 
of the text, removed some sentences, and rewritten several paragraphs 
in order to avoid repetition, and also to make them shorter, clearer, 
and easier to comprehend.

Also, all the tables of results have been moved to the Appendix and 
that data has been presented now in Subsection 5.2 and Section 6 
as the new Figures 2, 4, 5 and 6.

@@

\begin{verbatim}
[53] G.B. Huang, Q.Y. Zhu, C.K. Siew, Extreme learning machine: 
theory and applications, Neurocomputing 70 (1) (2006) 489-501.

[54] G. Huang, G.B. Huang, S. Song, K. You, Trends in extreme 
learning machines: a review, Neural Networks 61 (2015) 32-48.

[60] Wikipedia, List of Dewey decimal classes, [Online; accessed 
05-May-2016]. https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes

[71] M. A. Hall, Correlation-based feature selection for discrete 
and numeric class machine learning, in: Proceedings of the 
Seventeenth International Conference on Machine Learning, ICML2000, 
Morgan Kaufmann Publishers Inc., San Francisco, CA, USA, 2000, 
pp. 359-366.

[84] S. Ding, N. Zhang, X. Xu, L. Guo, J. Zhang, Deep extreme 
learning machine and its application in eeg classification, 
Mathematical Problems in Engineering 2015.

### 2016-09-10 paper.tex
completed responses to reviewer-1

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.4]{./imgs/prediction_all_publisher_all_features_Table3.eps}
\end{center}
\caption{Barplots showing the values obtained predicting \texttt{total\_sales}, including errorbars, with different regression methods (30 repetitions, 10-fold cross validation). All publishers and all the features have been considered.}
% Antonio - Should we explain the meaning of the dot and the small lines in every barplot? I guess they are mean and standard deviation, aren't they?
\label{fig:all_publishers_no_fs}
\end{figure*}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.42]{./imgs/prediction_all_publisher_Table5.eps}
\end{center}
\caption{Barplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation). All publishers and just those features selected by each method have been considered in every case.}
\label{fig:results_all_publishers_fs}
\end{figure*}

@@

\begin{table*}
\caption{Description of publishing companies considered as special cases.}
\centering{}%
\resizebox{14cm}{!}{
\begin{tabular}{|c|l|l|l|}
\hline 
 Case & Different books sold & Total copies sold & Description\\
\hline 
\textit{All publishing companies} & 6083 & 3201645 & 209 publishing companies\\
\hline 
\textit{UDL929} & 216 & 460752 & Best selling publishing company\\
\hline 
\textit{UDLW12} & 97 & 2635 & Mid-range selling publishing company\\
\hline 
\textit{UDL704} & 293 & 58236 & publishing company with most different\\ 
       &     &       & books sold\\
\hline 
\textit{UDLU11} & 180 & 249481 & publishing company with medium number\\ 
       &     &       &  of different books sold\\
\hline 
\end{tabular}
}
\label{Table:special_cases}
\end{table*}

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.6]{./imgs/attribute_All.eps}
\end{center}
\caption{Barplots showing the values obtained predicting
  \texttt{total\_sales}, using all features, with different regression
  methods (30 repetitions, 10-fold cross validation). Results obtained
  for different special publishing companies: UDL929 (the best selling
  publishing company), UDLW12 (the median selling publishing company),
  UDL704 (highest number of different titles sold) and UDLU11 (medium
  number of different books sold). 
}
\label{fig:attributeAll}
\end{figure*}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.6]{./imgs/attribute_ReliefFAttributeEval-FS.eps}
\end{center}
\caption{Barplots showing the values obtained predicting \texttt{total\_sales}, considering just the features selected by ReliefFAttributeEval method, with different regression methods (30 repetitions, 10-fold cross validation). Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).
}
\label{fig:casesReliefFAttributeEval}
\end{figure*}

>>>>

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.38]{./imgs/prediction_all_publisher_all_features_Table3.eps}
\end{center}
\caption{Barplots showing the values obtained predicting \texttt{total\_sales}, including errorbars, with different regression methods (30 repetitions, 10-fold cross validation). All publishers and all the features have been considered.}
% Antonio - Should we explain the meaning of the dot and the small lines in every barplot? I guess they are mean and standard deviation, aren't they?
\label{fig:all_publishers_no_fs}
\end{figure*}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.40]{./imgs/prediction_all_publisher_Table5.eps}
\end{center}
\caption{Barplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation). All publishers and just those features selected by each method have been considered in every case.}
\label{fig:results_all_publishers_fs}
\end{figure*}

@@

\begin{table*}
\caption{Description of publishing companies considered as special cases.}
\centering{}%
\resizebox{14cm}{!}{
\begin{tabular}{|c|l|l|l|}
\hline 
 Case & Different books sold & Total copies sold & Description\\
\hline 
\textit{All publishing companies} & 6083 & 3201645 & 209 publishing companies\\
\hline 
\textit{UDL929} & 216 & 460752 & Best selling publishing company\\
\hline 
\textit{UDLW12} & 97 & 2635 & Mid-range selling publishing company\\
\hline 
\textit{UDL704} & 293 & 58236 & Publishing company with most different\\ 
       &     &       & books sold\\
\hline 
\textit{UDLU11} & 180 & 249481 & Publishing company with medium number\\ 
       &     &       &  of different books sold\\
\hline 
\end{tabular}
}
\label{Table:special_cases}
\end{table*}

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.58]{./imgs/attribute_All.eps}
\end{center}
\caption{Barplots showing the values obtained predicting
  \texttt{total\_sales}, using all features, with different regression
  methods (30 repetitions, 10-fold cross validation). Results obtained
  for different special publishing companies: UDL929 (the best selling
  publishing company), UDLW12 (the median selling publishing company),
  UDL704 (highest number of different titles sold) and UDLU11 (medium
  number of different books sold). 
}
\label{fig:attributeAll}
\end{figure*}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.58]{./imgs/attribute_ReliefFAttributeEval-FS.eps}
\end{center}
\caption{Barplots showing the values obtained predicting \texttt{total\_sales}, considering just the features selected by ReliefFAttributeEval method, with different regression methods (30 repetitions, 10-fold cross validation). Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).
}
\label{fig:casesReliefFAttributeEval}
\end{figure*}
